Abstract Binding Trees

### 2015-10-27 paper.tex
Formatting
Add explanation of signature endofunctor & initial algebra

\DeclareMathOperator\Yoneda{\mathbf{y}}

@@

\subsection{Signatures and substitution monoidal structures}

@@

The presheaf of variables $\Define{V(\Upsilon\parallel\Gamma\vdash s)}{\MkSet{x \in \Dom\Gamma
\mid \Gamma(x) = s}}$ is the unit to this tensor, and together they comprise a
substitution monoidal structure. Then, a presheaf $A$ is a monoid if it is
equipped with the following natural transformations:

@@

>>>>

\newcommand\SigFun[1]{\mathcal{F}_{#1}}

@@

\subsection{Substitution monoidal structures}

@@

The presheaf of variables $\Define{V(\Upsilon\parallel\Gamma\vdash s)}{\MkSet{x \in \Dom\Gamma
\mid \Gamma(x) = s}}$ is the unit to this tensor, and together they comprise a
\emph{substitution monoidal structure}. Then, a presheaf $A$ is a monoid if it is
equipped with the following natural transformations:

@@

\subsection{The signature endofunctor and its initial algebras}

For each signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we have an
endofunctor $\Of{\SigFun{\Sigma}}{\Sets^\Seq\to\Sets^\Seq}$, which is defined
as follows:

\begin{align*}
  \IMode{\SigFun{\Sigma}(X)(\Upsilon\parallel\Gamma\vdash s)}
    &\triangleq
    \OMode{
      \coprod_{\vartheta\in\Operators\Pair{\Upsilon}{\MkArity{\vec{v}}{s}}}
      \prod_{\MkValence{\vec{p}}{\vec{q}}{s'}\in\vec{v}}
      X(\Upsilon,\vec{p}\parallel\Gamma,\vec{q}\vdash s')
    }
\end{align*}

%% TODO: in the above, \vec{q} is a list of sorts, but we need to pick out symbol
%% names for these before we can extend \Upsilon! Or do we?

Then, a $\Sigma$-model is a monoid $A$ which is equipped with an initial
algebra $\Of{\alpha}{\SigFun{\Sigma}(A)\to A}$, which shall interpret
applications of each operator.
